04_analysis

### 2023-12-08 05_analysis.Rmd
Update 05_analysis.Rmd
added ships to rolling plots

Original data points plotted
```{r}
ZC_pivot_reg <- pivot_longer(ZC_filt, cols = c(TOL_125,TOL_2000, Wpresence), names_to = "datacol", values_to = "value")

# Regular plotted detections
ggplot(ZC_pivot_reg, aes(x = UTC, y = value, color = datacol)) + geom_point(size = 0.1) +
  facet_grid(vars(datacol), scales = "free") +
  scale_x_datetime(date_breaks = "3 days") +
  theme(axis.text.x = element_text(angle = 90,
                                   vjust = 0.5, hjust=1)) +
  labs(title = "ZC Detections + SS Metrics - Buoy 21")

ggplot(ZC_pivot_reg, aes(x = UTC, y = value, color = datacol)) + geom_line() +
  facet_grid(vars(datacol), scales = "free") +
  scale_x_datetime(date_breaks = "3 days") +
  theme(axis.text.x = element_text(angle = 90,
                                   vjust = 0.5, hjust=1)) +
  labs(title = "ZC Detections + SS Metrics + Ships - Buoy 13")

>>>>

Original data points plotted
```{r fig.width = 12}
ZC_filt <- GPSwhaleAISenvSS10 %>% 
  filter(species %in% c("ZC", NA)) %>%
  # Hourly rolling averages
  mutate(rollAvg_Whl = zoo::rollapply(Wpresence, 5, mean, fill = NA)) %>%
  mutate(rollAvg_2000 = zoo::rollapply(TOL_2000, 5, mean, fill = NA)) %>%
  mutate(rollAvg_125 = zoo::rollapply(TOL_125, 5, mean, fill = NA)) %>%
  mutate(rollAvg_ship = zoo::rollapply(shipin10km, 5, mean, fill = NA)) %>%
  # Drop first and last NAs that are created as part of averages
  drop_na(., rollAvg_Whl)

ZC_pivot_reg <- pivot_longer(ZC_filt, cols = c(TOL_125,TOL_2000, Wpresence, shipin10km), names_to = "datacol", values_to = "value")

# Regular plotted detections
ggplot(ZC_pivot_reg, aes(x = UTC, y = value, color = datacol)) + geom_point(size = 0.1) +
  facet_grid(vars(datacol), scales = "free") +
  scale_x_datetime(date_breaks = "3 days") +
  theme(axis.text.x = element_text(angle = 90,
                                   vjust = 0.5, hjust=1)) +
  labs(title = "ZC Detections + SS Metrics + Ships - Buoy 10")

ggplot(ZC_pivot_reg, aes(x = UTC, y = value, color = datacol)) + geom_line() +
  facet_grid(vars(datacol), scales = "free") +
  scale_x_datetime(date_breaks = "3 days") +
  theme(axis.text.x = element_text(angle = 90,
                                   vjust = 0.5, hjust=1)) +
  labs(title = "ZC Detections + SS Metrics + Ships - Buoy 10")
